

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
setwd(here())
```

```{r data setup, include=FALSE}
pathfinderw <- read.csv('pathfinder.csv')
pathfinderw <- pathfinderw[1,1]
setwd(pathfinderw)
metaw <- read.csv('meta.csv')
varsw <- metaw[1,1]
timespecw <- metaw[2,1]
timenamew <- metaw[3,1]
spatialspecw <- metaw[4,1]
simple_summaryw  <- read.csv('simple_summary.csv')
boundsw  <- read.csv('bounds.csv')
complete_sharew  <- read.csv('complete_share.csv')
year_boundw  <- read.csv('year_bound.csv')
reg_completenessw  <- read.csv('reg_completeness.csv')
reg_year_sharew  <- read.csv('reg_year_share.csv')
regs_zero_compw  <- read.csv('regs_zero_comp.csv')
regs_zero_compw <- regs_zero_compw[,1] %>% as.vector()
regs_q1_compw <- read.csv('regs_q1_comp.csv')
regs_q1_compw <- regs_q1_compw[,1] %>% as.vector()
regs_q2_compw <- read.csv('regs_q2_comp.csv')
regs_q2_compw <- regs_q2_compw[,1] %>% as.vector()
regs_q3_compw  <- read.csv('regs_q3_comp.csv')
regs_q3_compw <- regs_q3_compw[,1] %>% as.vector()
regs_q4_compw  <- read.csv('regs_q4_comp.csv')
regs_q4_compw <- regs_q4_compw[,1] %>% as.vector()
regs_total_compw  <- read.csv('regs_total_comp.csv')
regs_total_compw <- regs_total_compw[,1] %>% as.vector()
regs_comp_summaryw  <- read.csv('regs_comp_summary.csv')
anom_lesserw <- read.csv('anom_lesser.csv')
lesser_count <- nrow(anom_lesserw)
anom_greaterw <- read.csv('anom_greater.csv')
greater_count <- nrow(anom_greaterw)
anom_exactw <- read.csv('anom_exact.csv')
exact_count <- nrow(anom_exactw)
anom_increasew <- read.csv('anom_increase.csv')
increase_count <- nrow(anom_increasew)
anom_decreasew <- read.csv('anom_decrease.csv')
decrease_count <- nrow(anom_decreasew)
paramsw <- read.csv('anomaly_parameters.csv')
metacompletew <- read.csv('metadata_completeness.csv')
setwd(here())
```


# Aggregation Report for `r varsw` in `r spatialspecw` `r timenamew`

\vspace{2cm}

## Simple Summary Statistics


```{r simple summary}
simple_summaryw
```
\vspace{.5cm}

The skewness of `r varsw` is __`r round(simple_summaryw$skew,2)`__ which is 
considered __`r if(simple_summaryw$skew > 5){"High"}else {"Acceptable"}`__

\vspace{.1cm}

`r varsw` is present in the data for __`r nrow(year_boundw)`__ years, first appearing
in __`r min(year_boundw)`__ and most recently appearing in __`r max(year_boundw)`__.

\vspace{.1cm}

Below is a visualization of the distribution of `r varsw`.

\vspace{.5cm}

```{r pathmake, include = FALSE}
distpath <- paste0(pathfinderw, "/Distribution.png")
yearpath <- paste0(pathfinderw, "/Yearly_Completeness.png")
comppath <- paste0(pathfinderw, "/Completeness_Distribution.png")
```


![](`r distpath`)

\vspace{.5cm}

## Completeness

\vspace{.1cm}

On average, a given year for `r varsw` will have __`r mean(complete_sharew$complete_share)`__ of
its regions holding data and not being NA. Below is a visualization of data completeness
over time.

\vspace{.1cm}

![ ](`r yearpath`)

\vspace{.1cm}

Spatially, __`r regs_comp_summaryw[1,2]`__ countries have no data for `r varsw`, 
__`r regs_comp_summaryw[2,2]`__ have between 0 and 25%, __`r regs_comp_summaryw[3,2]`__ have between 25% and 50% completion, __`r regs_comp_summaryw[4,2]`__ have between 50% and 75%, __`r regs_comp_summaryw[5,2]`__ between 75% and 99% and __`r regs_comp_summaryw[6,2]`__ have data
for every single year `r varsw` is present. This is visualized below.

\vspace{.1cm}

![ ](`r comppath`)

\vspace{.1cm}

Countries with no data are:

```{r no data}
regs_zero_compw
```


Countries with 0-25% data are:

```{r .25 data}
regs_q1_compw
```


Countries with 25% - 50% data are:

```{r .5 data}
regs_q2_compw
```


Countries with 50% - 75% data are:

```{r .75 data}
regs_q3_compw
```


Countries with 75% - 99% data are:

```{r .99 data}
regs_q4_compw
```


Countries with 100% data are:

```{r 100 data}
regs_total_compw
```

\vspace{.1cm}

Graphs with the total completion for country can be found in the Completion PNG
folder under `Country Totals` while completeness over time for each individual
country can be found under `year totals` - raw data for completeness over time 
for each region is available in the analysis_data folder, `reg_completeness.csv`

## Anomalies and Outliers

\vspace{.1cm}

The following are the parameters specified for `r varsw`:

\vspace{.1cm}

```{r parameters}
paramsw
```

\vspace{.1cm}

### Values lower than expected

\vspace{.1cm}

`r if(is.na(paramsw[1,2])){paste0("There was no specified minimum threshold for ", varsw)} else{paste0("There are ", lesser_count, " values present below the specified anomaly threshold of ", paramsw[1,2], ". Below are a list of the first ten - the full list is available in anom_lesser.csv.")}`

\vspace{.1cm}

```{r lessers}
if(is.na(paramsw[1,2])){}else{head(anom_lesserw,10)}
```

\vspace{.1cm}

### Values higher than expected

\vspace{.1cm}

`r if(is.na(paramsw[2,2])){paste0("There was no specified maximum threshold for ", varsw)} else{paste0("There are ", greater_count, " values present above the specified anomaly threshold of ", paramsw[2,2], ". Below are a list of the first ten - the full list is available in anom_greater.csv.")}`

\vspace{.1cm}

```{r greaters}
if(is.na(paramsw[2,2])){}else{head(anom_greaterw,10)}
```

\vspace{.1cm}

### Flagged values

\vspace{.1cm}

`r if(is.na(paramsw[3,2])){paste0("There was no specified flagged value for ", varsw)} else{paste0("There are ", exact_count, " flagged values present matching ", paramsw[3,2], ". Below are a list of the first ten - the full list is available in anom_exact.csv.")}`

\vspace{.1cm}

```{r exacts}
if(is.na(paramsw[3,2])){}else{head(anom_exactw,10)}
```

\vspace{.1cm}

### Unexpectedly high increase

\vspace{.1cm}

`r if(is.na(paramsw[4,2])){paste0("There was no specified maximum increase for ", varsw)} else{paste0("There are ", increase_count, " values with an increase over the previous value above the anomaly threshold of ", paramsw[4,2], ". Below are a list of the first ten - the full list is available in anom_increase.csv.")}`

\vspace{.1cm}

```{r increases}
if(is.na(paramsw[4,2])){}else{head(anom_increasew,10)}
```

\vspace{.1cm}

### Unexpectedly high decrease

\vspace{.1cm}

`r if(is.na(paramsw[5,2])){paste0("There was no specified maximum decrease for ", varsw)} else{paste0("There are ", decrease_count, " values with a decrease from the previous value below the anomaly threshold of ", paramsw[5,2], ". Below are a list of the first ten - the full list is available in anom_decrease.csv.")}`

\vspace{.1cm}

```{r decreases}
if(is.na(paramsw[5,2])){}else{head(anom_decreasew,10)}
```

\vspace{.1cm}


## Metadata and Licensing

\vspace{.1cm}

The following is the status of the metadata for `r varsw`:

\vspace{.1cm}

```{r}
metacompletew
```

\vspace{.3cm}

__End of Report__

